---
title: "NLP with NASA Metadata"
author: "*Seolmin Yang*"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "2023-02-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = F)
```

## Introduction
This work aims to practice NLP and text analysis by using the NASA metadata. NASA provides over 32,000 datasets as a form of metadata, such as title, description, and keywords. I adopt the tutorial codes provided by Julia Silge and David Robinson in their book, Text Mining with R (see <https://www.tidytextmining.com/index.html>).

[Getting the NASA metadata](#getting-the-nasa-metadata)   
[Tyding the keywords from NASA metadata](#tyding-the-keywords-of-the-nasa-metadata)   
[Keyword co-occurrences and correlations](#keyword-co-occurrences-and-correlations)   

## Getting the NASA metadata

The NASA metadata has JSON format.
```{r getting}
library(jsonlite)
metadata = fromJSON("https://data.nasa.gov/data.json")
names(metadata$dataset)
```

## Tyding the keywords of the NASA metadata

I mainly focus on the keywords of the NASA metadata. Using tidytext's unnest(), I break the text to make a tidy data structure.
```{r tyding}
library(dplyr)
library(tidyr)
library(tidytext)
nasa_keyword = tibble(id = metadata$dataset$identifier,
                      keyword = metadata$dataset$keyword) %>% 
  unnest(keyword)

nasa_keyword
```


## Keyword co-occurrences and correlations
I calculate co-occurrences and correlations of keywords

```{r co-occurrence}
library(widyr)

keyword_pairs = nasa_keyword %>% 
  pairwise_count(keyword, id, sort = T, upper = F)

keyword_pairs
```

```{r correlation}
keyword_cors = nasa_keyword %>% 
  group_by(keyword) %>% 
  filter(n() >= 200) %>% 
  pairwise_cor(keyword, id, sort = T, upper = F)

keyword_cors
```

Then, I plot the co-occurrence network of the keywords.

```{r co-occurence network, warning = F}
library(ggraph)
library(igraph)

set.seed(123)
keyword_pairs %>% 
  filter(n >= 700) %>% 
  graph_from_data_frame() %>% 
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n),
                 edge_colour = "royalblue") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = T,
                 point.padding = unit(0.2, "lines")) +
  labs(title = "Keyword co-occurence network") +
  theme_void()
```

This is the correlation network of the keywords.

```{r correlation network, warning = F}
set.seed(123)
keyword_cors %>% 
  filter(correlation > .6) %>% 
  graph_from_data_frame() %>% 
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation),
                 edge_colour = "royalblue") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = T,
                 point.padding = unit(0.2, "lines")) +
  labs(title = "Keyword correlation network") +
  theme_void()
```
